---
title: "Automated Report"
output:
  pdf_document: default
  html_document: default
---

##Introduction

This is an example of automating reports, the code below shows the part of the R code where the user enters information for the report:
```{r Set year, country & filename for report, include=TRUE}
# Set year and country to create report for, name of the country and filename 
# (including .xls or .xlsx), must be inside the ""!!, if several years put in : between 
# (for example 1990:2000)
chosen_year <- 1990:2000
chosen_country <- "Sweden"
filename <- "indicator_t 25-54 unemploy.xlsx"
# Set indicator, must be within the ""!!
indicator <- "Unemployment rate"
########################################################################################
```


```{r load packages and set options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(readxl)
library(knitr)
```

```{r import and prepare data, include=FALSE}
location <- here()
unemployment <- read_excel(paste0(location, "/", filename))
unemployment_long <- gather(unemployment, year, rate, -country)
```

\pagebreak

## Gapminder Report

  
Link to the data used in this report <https://www.gapminder.org/data/>.


This is an introductory text where country and year is automated automatically based on the information the user entered above, this example is for `r chosen_country` between `r min(chosen_year)` & `r max(chosen_year)`.
  
  
### Including Tables
```{r table, echo = FALSE, results = 'asis'}

kable(unemployment[unemployment$country == chosen_country, c("country", as.character(chosen_year))], caption = paste(indicator, "for", chosen_country, "between the years", min(chosen_year), "&", max(chosen_year)))
```

### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
unemployment_long[unemployment_long$year %in% chosen_year & unemployment_long$country == chosen_country,] %>%
  ggplot(aes(x = as.numeric(year), y = rate, color = country)) +
  geom_line() +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(color = "Country", title = paste("Development of", indicator, "in", chosen_country, "between the years", min(chosen_year), "&", max(chosen_year)), caption = "Source: Gapminder") +
  xlab("Year") +
  ylab(paste(indicator)) +
  theme_bw()+
  theme(plot.title = element_text(size = 11))
```
